How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-14 tse-paper/content.tex
lacheck corrections

However, build logs can be verbose and large---sometimes in excess of
50 MB of ASCII text ~\cite{beller2017oops}---making them inadequate
for direct human consumption.
Therefore, to support developers and
researchers in efficiently making use of the information within build
logs, we must at least semi-automatically retrieve the chunks of the
log that describe the targeted information.

There are different techniques to retrieve information chunks from CI
build logs.
Beller et al.
use a rule-based system of regular
expressions to analyze logs from Travis CI~\cite{beller2017oops}.
Such regular expressions are developed by looking at exemplary build
logs.
Vassallo et al.\ wrote a custom parser to gather information
for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et
al.\ reduced the number of lines for a developer to inspect by
creating a diff between logs from failed and successful
builds~\cite{amar2019mining}.

@@

* What went wrong:
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
Could not determine the dependencies of task `:app:jacocoTestDebugReport'.
> Task with path 'testDebug' not found in project ':app'.
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A related field of build log analysis is the processing of system log
files produced during runtime.
A main difference between build logs
and system logs is that system logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
Figure \ref{lst:system-log} shows
example lines from a system log.

@@

The techniques developed for system log analysis can also be applied
to build logs.
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
%Classic log parsers interpret the whole log file into a sequence of
%events.
% A similar approach could also be applied to build logs to
%determine the sequence of executed build steps or phases.
In this article, we focus on extracting a single specified information
from the build log as a whole with chunk retrieval techniques.
Chunk
retrieval techniques are used as a part of log parsing to retrieve the
values of variable parts in a log message, e.g.
by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.
Note that for most questions we allowed assigning multiple values, e.g.
if
two kinds of informations were targeted during a build log analysis.

@@

The articles classified the build logs into categories in 36\% of
the cases.
Didrik Lindqvist~\cite{lindqvist2019detection} used build logs to
distuinguish failures caused by
developers from those caused by infrastructure, while
Kavaler et al.~\cite{kavaler2019tool} idenfity projects that use
automated static analysis tools.
Other types of information (e.g.
counting lines, summarization) were only retrieved
in one case each.

@@

\subsection{Common Text Similarity (CTS)}
\label{sec:expl-ts}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts
~\cite{runeson2007detection,marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique based on the common
and simple Vector Space Model~\cite{schutze2008introduction}.
The aim is to retrieve those lines from a build log which are most
similar to examples given by the user.
% Text Similarity approaches are used to filter unstructured textual
% software artifacts.
% One common technique
% %
%artifacts.
% % One common and simple technique is the Vector Space Model.
% We
% % investigate when text similarity is a suitable technique to retrieve
% % information chunks from build logs.
% In the following we will explain
% % the concept of how we apply text similarity to information retrieval
% % from CI build logs, which we refer to as \emph{CTS}\@.

@@

\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
evaluation.
Out of the 400 runs, 5 per each one of the 80 example
sets, PBE extracted all the desired lines in 138 cases.
In 89 further
cases, an extraction program was also successfully synthesized, though
in 59 of the 89 cases the synthesized program yielded no output.
In 30
of the 89 cases did the synthesized program only partially extract a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
Listing \ref{lst:pbe-unsuccessful} shows an example of such
an \emph{unsuccessful retrieval}, where the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize program consistent with all of the training
examples.

@@

If the information chunks are from multiple structural categories,
i.e.
they are not represented in the same structural way within the
build logs, and recall is more important than precision we recommend
to use KWS\@.
If the representations are from multiple structural
categories and precision is more important than recall to the user we
recommend CTS\@.
We also recommend CTS when the representations are
from one structural category, when the user does not require a high
confidence in the precision or recall of the outcome and when the user
would rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user
wishes a high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

As a final recommendation, one could create a ``super analyzer'' by
combining the different build log analysis techniques studied in this
paper.
Such a super analyzer would likely always first employ PBE
(because of its high accuracy), followed by a combination of CTS and
KWS.
Other than initial setup and training time, there should be no
downside to this approach if it is implemented in a transparent way to
the underlying technique: the output of the super analyzer could
include from which sub-tool it originated and thus facilitate
automatic on-ward processing or interpretation of the result.

>>>>

However, build logs can be verbose and large---sometimes in excess of
50 MB of ASCII text~\cite{beller2017oops}---making them inadequate
for direct human consumption.
Therefore, to support developers and
researchers in efficiently making use of the information within build
logs, we must at least semi-automatically retrieve the chunks of the
log that describe the targeted information.

There are different techniques to retrieve information chunks from CI
build logs.
Beller et al.\ use a rule-based system of regular
expressions to analyze logs from Travis CI~\cite{beller2017oops}.
Such regular expressions are developed by looking at exemplary build
logs.
Vassallo et al.\ wrote a custom parser to gather information
for build repair hints~\cite{vassallo2018un-break}.
Recently, Amar et
al.\ reduced the number of lines for a developer to inspect by
creating a diff between logs from failed and successful
builds~\cite{amar2019mining}.

@@

* What went wrong:
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[backgroundcolor=\color{Cerulean!60},breaklines=true,frame=rl]
Could not determine the dependencies of task ':app:jacocoTestDebugReport'.
> Task with path 'testDebug' not found in project ':app'.
  \end{lstlisting}
  \vspace{-\baselineskip}
  \begin{lstlisting}[breaklines=true,frame=blr]

@@

\subsection{Distinction from System Log Analysis}
\label{sec:system-log-analysis}
A related field of build log analysis is the processing of system log
files produced during runtime.
A main difference between build logs
and system logs is that system logs are fundamentally structured
through events.
Each line in a log file represents one event with a
set of fields: timestamp, verbosity level and raw message
content~\cite{he2017towards}.
\Cref{lst:system-log} shows
example lines from a system log.

@@

The techniques developed for system log analysis can also be applied
to build logs.
One example is comparing execution traces to reference
traces of intended behavior to detect anomalies.
Amar et
al.~\cite{amar2019mining} employed a similar approach to detect
relevant lines in build logs.
%Classic log parsers interpret the whole log file into a sequence of
%events.
% A similar approach could also be applied to build logs to
%determine the sequence of executed build steps or phases.
In this article, we focus on extracting a single specified information
from the build log as a whole with chunk retrieval techniques.
Chunk
retrieval techniques are used as a part of log parsing to retrieve the
values of variable parts in a log message, e.g.\ by using regular
expressions~\cite{nagappan2010abstracting,xu2009detecting}.

@@

The full data extraction template and our results of this step can be
found in our replication package~\cite{brandt2020chunk-replication}.
Note that for most questions we allowed assigning multiple values,
e.g.\ if
two kinds of informations were targeted during a build log analysis.

@@

The articles classified the build logs into categories in 36\% of
the cases.
Didrik Lindqvist~\cite{lindqvist2019detection} used build logs to
distuinguish failures caused by
developers from those caused by infrastructure, while
Kavaler et al.~\cite{kavaler2019tool} idenfity projects that use
automated static analysis tools.
Other types of information (e.g.\ counting
lines, summarization) were only retrieved
in one case each.

@@

\subsection{Common Text Similarity (CTS)}
\label{sec:expl-ts}
Text Similarity approaches are widely used to filter unstructured
textual software artifacts~\cite{runeson2007detection,
marcus2005recovery,antoniol2002recovering,mccarey2006recommending}.
We investigate a chunk retrieval technique based on the common
and simple Vector Space Model~\cite{schutze2008introduction}.
The aim is to retrieve those lines from a build log which are most
similar to examples given by the user.
% Text Similarity approaches are used to filter unstructured textual
% software artifacts.
% One common technique
% %
%artifacts.
% % One common and simple technique is the Vector Space Model.
% We
% % investigate when text similarity is a suitable technique to retrieve
% % information chunks from build logs.
% In the following we will explain
% % the concept of how we apply text similarity to information retrieval
% % from CI build logs, which we refer to as \emph{CTS}\@.

@@

\Cref{fig:failure-reason-PBE} shows the results of the PBE runs in our
evaluation.
Out of the 400 runs, 5 per each one of the 80 example
sets, PBE extracted all the desired lines in 138 cases.
In 89 further
cases, an extraction program was also successfully synthesized, though
in 59 of the 89 cases the synthesized program yielded no output.
In 30
of the 89 cases did the synthesized program only partially extract a
subset of the desired lines.
For these 30 cases, the average recall
was 28\%.
\Cref{lst:pbe-unsuccessful} shows an example of such
an \emph{unsuccessful retrieval}, where the synthesized program only
retrieved two of the four targeted lines.
In 173 of the 400 cases
could PROSE not synthesize program consistent with all of the training
examples.

@@

If the information chunks are from multiple structural categories,
i.e.\ they are not represented in the same structural way within the
build logs, and recall is more important than precision we recommend
to use KWS\@.
If the representations are from multiple structural
categories and precision is more important than recall to the user we
recommend CTS\@.
We also recommend CTS when the representations are
from one structural category, when the user does not require a high
confidence in the precision or recall of the outcome and when the user
would rather have output with low recall instead of no output at all.
When the representations are from one structural category and the user
wishes a high confidence in the correctness of the output or prefers
no output over output with low recall, we recommend PBE\@.

As a final recommendation, one could create a ``super analyzer'' by
combining the different build log analysis techniques studied in this
paper.
Such a super analyzer would likely always first employ PBE
(because of its high accuracy), followed by a combination of CTS and
KWS\@.
Other than initial setup and training time, there should be no
downside to this approach if it is implemented in a transparent way to
the underlying technique: the output of the super analyzer could
include from which sub-tool it originated and thus facilitate
automatic on-ward processing or interpretation of the result.
